quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-18 paper-quollr.Rmd
Initial update for implementation section
Initial work on the quollr implementation

The implementation of `quollr` emphasizes modularity, computational efficiency, and interoperability.
Its design follows a layered architecture that separates **data preprocessing**, **model construction**, and **visualization**, ensuring clarity, extensibility, and compatibility with the wider R ecosystem.

>>>>

The implementation of `quollr` is designed to be modular, efficient, and easy to extend. The package is organized into a series of logical components that reflect the main stages of the workflow: data preprocessing, model fitting, low-density bin removal, prediction, visualization, and interactive exploration. This modular structure makes the code easier to maintain and allows new features to be added without disrupting the existing functionality.

### 2025-10-18 paper-quollr.tex
Initial update for implementation section
Initial work on the quollr implementation

The implementation of \texttt{quollr} emphasizes modularity, computational efficiency, and interoperability.
Its design follows a layered architecture that separates \textbf{data preprocessing}, \textbf{model construction}, and \textbf{visualization}, ensuring clarity, extensibility, and compatibility with the wider R ecosystem.

>>>>

The implementation of \texttt{quollr} is designed to be modular, efficient, and easy to extend. The package is organized into a series of logical components that reflect the main stages of the workflow: data preprocessing, model fitting, low-density bin removal, prediction, visualization, and interactive exploration. This modular structure makes the code easier to maintain and allows new features to be added without disrupting the existing functionality.
